---
title: "Assignment 7"
author: "Eric Tu"
date: "9/29/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("xlsx")
library("lmtest")
```

## Load GPD Data

```{r data}
data <- read.xlsx("Case_GDP.xls", 1)
head(data)
```

## Part a

### Likelihood Ratio tests
$b_{0}$ is parameters with restriction
$b_{1}$ is parameters w/o restriction

Chi-square distribution
LR = $ -2 (\log L(b_{0}) - \log L(b_{1}))$

```{r Likelihood}
# Storing given log likelihood values
## Restricted Models
ll_b0_c <- -152.763
ll_b0_c_li1 <- -139.747
ll_b0_c_li2 <- -149.521

## Unrestriced model
ll_b1 <- -134.178

# Storing number of restrictions
m_b0_c <- 2
m_b0_c_li1 <- 1
m_b0_c_li2 <- 1

# Test log likelihood ratio
llr <- function(ll0, ll1){
  -2 * (ll0 - ll1)
}

llr_b0_c <- llr(ll_b0_c, ll_b1)
llr_b0_c_li1 <- llr(ll_b0_c_li1, ll_b1)
llr_b0_c_li2 <- llr(ll_b0_c_li2, ll_b1)

# Critical values chi-square
prob <- 0.95
crit_b0_c <- qchisq(prob, df = m_b0_c)
crit_b0_c_li1 <- qchisq(prob, df=m_b0_c_li1)
crit_b0_c_li2 <- qchisq(prob, df = m_b0_c_li2)

# Significant Bool
sig_b0_c <- (llr_b0_c > crit_b0_c)
sig_b0_c_li1 <- (llr_b0_c_li1 > crit_b0_c_li1)
sig_b0_c_li2 <- (llr_b0_c_li2 > crit_b0_c_li2)


```

For Joint Li1, Li2. Log Likelihood ratio: `r llr_b0_c` Crit Val: `r crit_b0_c` Significant: `r sig_b0_c`

For Li1. Log Likelihood ratio: `r llr_b0_c_li1` Crit Val: `r crit_b0_c_li1` Significant: `r sig_b0_c_li1` 

For Li2. Log Likelihood ratio: `r llr_b0_c_li2` Crit Val: `r crit_b0_c_li2` Significant: `r sig_b0_c_li2`


## Part b
We can use McFadden $R^{2}$ to select the best lag structure because all the log likelihood ratios are significant. The McFadden $R^{2}$ calculation is given by $R^{2} = 1 - \cfrac{\log{L(b)}}{\log{L(b_{1})}}$ where $b_{1}$ is the model with only an intercept. The largest Mcfadden $R^{2}$ value should be chosen as the preferred logit model.

```{r Mcfadden}
calcMcfadden <- function(ll_test, ll_const){
  1 - ll_test/ll_const
}

ll_logit1 <- -134.178
ll_logit2 <- -134.126
ll_logit3 <- -130.346
ll_logit4 <- -130.461
ll_const <- -152.763

mc_r2_logit1 <- calcMcfadden(ll_logit1, ll_const)
mc_r2_logit2 <- calcMcfadden(ll_logit2, ll_const)
mc_r2_logit3 <- calcMcfadden(ll_logit3, ll_const)
mc_r2_logit4 <- calcMcfadden(ll_logit4, ll_const)
```

The Mcfadden $R^{2}$ values are:

* Logit 1 [li1(-1), li2(-1)]: `r mc_r2_logit1`
* Logit 2 [li1(-1), li2(-2)]: `r mc_r2_logit2`
* Logit 3 [li1(-2), li2(-1)]: `r mc_r2_logit3`
* Logit 4 [li1(-2), li2(-2)]: `r mc_r2_logit4`

The best model is Logit 3 [li1(-2), li2(-1): with the highest McFadden $R^{2}$ value of `r mc_r2_logit3`

## Part c

Logit Model 3:
$\beta_{c} = 0.746$
$\beta_{li1(-2)} = -0.429$
$\beta_{li2(-1)} = -0.131$

Pr[$y_{i} = 1$] = $\cfrac{exp(x_{i}'b)}{1 + exp(x_{i}'b)}$
Pr[$y_{i} = 0$] = $\cfrac{1}{1 + exp(x_{i}'b)}$

```{r LogitEval} 
beta_c <- 0.746
beta_1 <- -0.429
beta_2 <- -0.131
cutoff <- 0.5
range <- 245:264
x_1 <- data$li1[range]
x_2 <- data$li2[range]

Z <- exp(beta_c + beta_1 * x_1 + beta_2 * x_2)
logit_vals <- Z/(1 + Z) 
  
predic_num = as.integer(logit_vals > cutoff)

logit_eval <- data$GDPIMPR[range]
logit_num <- as.numeric(levels(logit_eval))[logit_eval]

t0_p0 <- sum((predic_num == 0 & logit_num == 0))/ length(range)
t0_p1 <- sum((predic_num == 1 & logit_num == 0))/ length(range)
t1_p0 <- sum((predic_num == 0 & logit_num == 1))/ length(range)
t1_p1 <- sum((predic_num == 1 & logit_num == 1))/ length(range)
```

<center>Cut-off value: 0.5</center>

observed | $\hat{y} = 0$  | $\hat{y} = 1$  | sum
-------- | -------------  | -------------  | ---
$y = 0$  | `r t0_p0`      | `r t0_p1`      | `r t0_p0+t0_p1`
$y = 1$  | `r t1_p0`      | `r t1_p1`      | `r t1_p0+t1_p1`
sum      | `r t0_p0+t1_p0`|`r t0_p1+t1_p1` | `r t0_p0+t1_p0+t0_p1 +t1_p1`
-----------------------------------------------
<center>Hit rate: `r t0_p0` + `r t1_p1` = `r t0_p0 + t1_p1` </center>

## Part d
Augmented Dicky-Fuller test on LOG GDP.
Includes constant, trend, and single lag.

```{r Dicky-Fuller}
est_range <- 4:242
log_gdp <- data$LOGGDP[est_range]
log_gdp_lag1 <- data$LOGGDP[est_range-1]
log_gdp_diff1 <- diff(data$LOGGDP)[est_range]
trend <- data$T[est_range]

df_fit <- lm(log_gdp~log_gdp_lag1+log_gdp_diff1+trend)


crit_val_trend <- -3.5

ro_coef <- summary(df_fit)$coef[3,1]
ro_tval <- summary(df_fit)$coef[3, 3]

reject_non_stationarity <- ro_tval < crit_val_trend
```

* Dicky-Fuller Test: `r ro_coef`
* Dicky-Fuller t-val: `r ro_tval`
* Reject Non-Stationary: `r reject_non_stationarity`
Confiremd Log gdp is not stationary

## Part e


``` {r linear_models}
fact2num <- function(fact){
  as.numeric(levels(fact))[fact]
}
growth_rate <- fact2num(data$GrowthRate[est_range])
growth_rate_lag1 <- fact2num(data$GrowthRate[est_range-1])
li1_lag1 <- data$li1[est_range-1]
li1_lag2 <- data$li1[est_range-2]
li2_lag1 <- data$li2[est_range-1]
li2_lag2 <- data$li2[est_range-2]

lm_logit1 <- lm(growth_rate~growth_rate_lag1+li1_lag1+li2_lag1)
lm_logit2 <- lm(growth_rate~growth_rate_lag1+li1_lag1+li2_lag2)
lm_logit3 <- lm(growth_rate~growth_rate_lag1+li1_lag2+li2_lag1)
lm_logit4 <- lm(growth_rate~growth_rate_lag1+li1_lag2+li2_lag2)

r2_logit1 <- summary(lm_logit1)$r.squared
r2_logit2 <- summary(lm_logit2)$r.squared
r2_logit3 <- summary(lm_logit3)$r.squared
r2_logit4 <- summary(lm_logit4)$r.squared

```

$R^{2}$ values are:

* Logit 1: [li1(-1), li2(-1)] `r r2_logit1`
* Logit 2: [li1(-1), li2(-2)] `r r2_logit2`
* Logit 3: [li1(-2), li2(-1)] `r r2_logit3`
* Logit 4: [li1(-2), li2(-2)] `r r2_logit4`

Coefficients for best model Logit 1 are
```{r coef}
summary(lm_logit1)$coef
```


## Part f
Breusch-Godfrey test on first-order residuals

```{r breusch-godfrey}
BG <- bgtest(growth_rate~growth_rate_lag1+li1_lag1+li2_lag1, type="Chisq")
#BG <- length(resid_logit2)*r2_resid
crit_BC <- qchisq(prob, df = 1)
BC_choice <- (BG$statistic < crit_BC)
```


Residuals look like white noise allowing characterization of BG test as chi-square distribution with # lags degrees of freedom.

* BG value: `r BG$statistic`
* Critical value: `r crit_BC`
* Model Correctly Specified: `r BC_choice`

## Part g
``` {r predict}
ind_gr_lag1 <- fact2num(data$GrowthRate[range-1])
ind_l1_lag1 <- data$li1[range-1]
ind_l2_lag1 <- data$li2[range-1]

indicators <- data.frame("growth_rate_lag1" = ind_gr_lag1, "li1_lag1" = ind_l1_lag1, "li2_lag1" = ind_l2_lag1)
predictions <- predict(lm_logit1, indicators)

plot(data$T[range], fact2num(data$GrowthRate[range]), col="blue", main="Actual vs Predicted Growth Rates")
points(data$T[range], predictions, col="red")

legend(x="topright", c("Prediction","Actual"),col=c("red","blue"),pch=c(1, 1))

MSE <- function(y1, y2){
  sum((y1 - y2) ** 2)/length(y1)
}

mse <- MSE(fact2num(data$GrowthRate[range]), predictions)

```
Mean squared error of: `r mse`