---
title: "Exercise4_4"
author: "Eric Tu"
date: "9/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("xlsx")
library("matlib")
```

## Data Loading
Let's load in the data first
```{r data}
data <- read.xlsx("TrainExer44.xls", 1)
head(data)
```

## Regress PG on Instruments, Part 1 of 2SLS
We are going to use a constant, RI, RPT, RPN, and RPU as instruments
Regress PG against the instrument
```{r instrument}
fit_instr <- lm(PG~RI + RPT + RPN + RPU, data=data)
val <- fit_instr$fitted.values
summary(fit_instr)
```

## Regress GC on Fitted X Values, Part 2 of 2SLS
With the exogenous fitted values
```{r 2sls}
fit <- lm(data$GC~val + data$RI)
summary(fit)
```

## Sargan test
Determine correlation between instruments and error
```{r Sargan}
fit_sargan <- lm(fit$residuals~data$RI + data$RPT + data$RPN + data$RPU)
nr2 <- nrow(data) * summary(fit_sargan)$r.squared
chisq.test(nr2)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
