---
title: "Exercise4_2"
author: "Eric Tu"
date: "9/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("xlsx")
library(knitr)
```

## Loading Data


```{r}
data <- read.xlsx("TrainExer42.xls", 1)
head(data)
```

## Part a

First consider the case where the event only directly affects price $(\alpha = 0)$. Estimate and report the price
coefficients under all 4 scenarios for $\beta$ and calculate the $R^{2}$
for all these regressions. Do the estimated price
coefficients signal any endogeneity problem for these values of $\alpha$ and $\beta$? Can you also explain the pattern you
find for the $R^{2}$?

For $\beta = 0$:
```{r}
fit <- lm(SALES0_0~PRICE0, data=data)
summary(fit)
```

```{r, echo=FALSE}
plot(data$PRICE0, data$SALES0_0, xlab='Price', ylab='Sales', main='beta=0')
abline(fit)
```

```{r, echo=FALSE}
kable(summary(fit)$coef)
```

For $\beta = 1$:
```{r}
fit <- lm(SALES0_1~PRICE1, data=data)
summary(fit)
```

```{r, echo=FALSE}
plot(data$PRICE1, data$SALES0_1, xlab='Price', ylab='Sales', main='beta=1')
abline(fit)
```

```{r, echo=FALSE}
kable(summary(fit)$coef)
```

For $\beta = 5$:
```{r}
fit <- lm(SALES0_5~PRICE5, data=data)
summary(fit)
```

```{r, echo=FALSE}
plot(data$PRICE5, data$SALES0_5, xlab='Price', ylab='Sales', main='beta=5')
abline(fit)
```

```{r, echo=FALSE}
kable(summary(fit)$coef)
```

For $\beta = 10$:
```{r}
fit <- lm(SALES0_10~PRICE10, data=data)
summary(fit)
```

```{r, echo=FALSE}
plot(data$PRICE10, data$SALES0_10, xlab='Price', ylab='Sales', main='beta=10')
abline(fit)
```

```{r, echo=FALSE}
kable(summary(fit)$coef)
```

## Part B

